### 2016-05-03 ch03-lrm/nonparametric.tex
Ch03: summary of simulations

  % \subsection{Implications of the model structure}
  % \subsection{Implications of the noise level}
  % \subsection{Implications of the noise coloring}

@@

\subsection{Summary}
\TODO{discussie}

@@

  % \section{Measurements}
  % \label{sec:measurements}
  %  \subsection{AVIS}
   % \subsection{F16}

\section{Trading off the bias and variance}

\TODO{introduction, probleem, oplossingen die besproken worden}

>>>>

  % \subsection{Implications of the model structure}
  % \subsection{Implications of the noise coloring}

@@

\subsection{Summary}
In general, it can be seen that the \gls{LRM} performs better than \gls{LPM} unless the \gls{SNR} near the resonance is very low ($10\unit{dB}$).
For the \gls{LPM}, it should be noted that near resonances,it more advantageous to use even model orders~\citep{Schoukens2013LPMerror}.
The results for the $\lpm{7,4,4}$ in the previous section are representative of the best-case performance of an $\lpm{7,\order{B},\order{A}}$ technique.
Concretely, for small $\nBW$, the dominant error in the \gls{LPM} is due to the bias.
Reducing the model order of the \gls{LPM} further will only increase the \gls{RMS} error.
Increasing the model order of the \gls{LPM} (e.g. to $\lpm{7,6,6}$) would result in an estimation where the residuals have very few degrees of freedom ($\DOF=1$ for $\lpm{7,6,6}$) such that estimated noise level is less reliable~\citep{Pintelon2010LPM1}.

For the \gls{LRM}, it can be seen that its model order as a significant influence on the approximation error.
In small datasets with high \gls{SNR} ($\SNR=60\unit{dB},\nBW<3$), and in datasets with low \gls{SNR} ($\SNR < 40 \unit{dB}$), selecting a better local model can reduce the bias significantly.
Nevertheless, the bias of the \gls{LRM} is only a significant contributor to the \gls{RMS} error for short datasets with low \gls{SNR}.
As such, selection of a better local model is only reduces the \gls{RMS} error for those settings.
Practically, this means that in most other settings of \gls{SNR} and frequency resolution, either a first-order or second-order \gls{LRM} ($\order{A},\order{B} \in \set{1,2}$) will perform almost equally well.
From an intuitive point of view: this works well when each local bandwidth $\LocalWindow$ is affected by at most two resonances.

The \gls{LRIC} is not practically viable due to the high variability.
However, since its bias is much lower than for the other methods, \gls{LRIC} offers perspectives for improving the overall performance significantly.

@@

\section{Trading off the bias and variance}
In the last section, it was illustrated that the model order of the local \gls{LRM} models, can significantly affect the obtained \gls{RMS} error.
This is specifically the case for small and noisy datasets.
Moreover, it was observed that the \gls{LRIC} has a high variance which might be due to pole-zero cancellations in the \gls{LRIC}.
As such, it makes sense to ask ourselves the question: ``can we determine a good local model order''?
That is the question we will investigate in this section.
First, some classical approaches are compared in the context of local modeling, i.e. relatively small (local) datasets.
